Convolutional Neural Nets for the MNIST Digit Dataset

### 2014-12-12 tex/paper.tex
Add info to experiments sectoin

The one convolutional/pooling layer architecture was trained for 50 iterations with 50 images per digit
(training set of 500 images), and was subsequently tested on
1,000 new images per digit (test set of 10,000 images).
The training images were taken from the easier portion of the training set, while the test images were taken from
both sets. The results of this training can be seen in Figure \ref{fig:accplot}. The test accuracy was recorded every five training
iterations. An example classification of an image along with the internal state of the trained network is depicted
in Figure \ref{fig:actfilts}. Figure [?] shows examples of correctly and incorrectly classified images.

@@

The second experiment with the one convolutional/pooling layer architecture was also trained
for 50 iterations but with 100 images per digit instead of 50 (training set of 1,000 images).
This trained network was then tested on 1,000 new images per digit (test set of 10,000 images).
The results of this training can be seen in Figure \ref{fig:accplot}.
The test accuracy was recorded every five training iterations.
Figure [?] shows examples of correctly and incorrectly classified images.

@@

The two convolutional/pooling layer architecture was also trained for 50 iterations with 50 images per digit
(training set of 500 images), and was subsequently tested on 1,000 new images per digit
(test set of 10,000 images).
The training images were taken from the easier portion of the training set,
while the test images were taken from both sets.
The results of this training can be seen in Figure \ref{fig:accplot}.
Again, the test accuracy was recorded every five training iterations.
An example classification of an image along with the internal state of the trained network is depicted in
Figure \ref{fig:actfilts}.
Figure [?] shows examples of correctly and incorrectly classified images.

>>>>

The one convolutional/pooling layer architecture was trained for 50 iterations with 50 images per digit
(training set of 500 images), and was subsequently tested on
1,000 new images per digit (test set of 10,000 images).
The training images were taken from the easier portion of the training set, while the test images were taken from
both sets. The results of this training can be seen in Figure \ref{fig:accplot}. The test accuracy was recorded every five training
iterations. This trained network achieved an accuracy of 94\% and very quickly converged after five iterations of training. An example 
classification of an image with the activations and learned filters is presented
in Figure \ref{fig:actfilts}. Figure [?] shows examples of correctly and incorrectly classified images.

@@

The second experiment with the one convolutional/pooling layer architecture was also trained
for 50 iterations but with 100 images per digit instead of 50 (training set of 1,000 images).
This trained network was then tested on 1,000 new images per digit (test set of 10,000 images).
The results of this training can be seen in Figure \ref{fig:accplot}.
The test accuracy was recorded every five training iterations. This trained network achieved an accuracy of 93.22\% and also quickly converged after about five iterations of training.
Figure [?] shows examples of correctly and incorrectly classified images.

@@

The two convolutional/pooling layer architecture was also trained for 50 iterations with 50 images per digit
(training set of 500 images), and was subsequently tested on 1,000 new images per digit
(test set of 10,000 images).
The training images were taken from the easier portion of the training set,
while the test images were taken from both sets.
The results of this training can be seen in Figure \ref{fig:accplot}.
Again, the test accuracy was recorded every five training iterations. This trained network achieved an accuracy of 92.8\% converging after about 10 iterations of training.
An example 
classification of an image with the activations and learned filters is presented
in Figure \ref{fig:actfilts}.
Figure [?] shows examples of correctly and incorrectly classified images.
